High-Dimensional Regularized Discriminant Analysis

### 2017-10-19 reports/paper-hdrda.Rnw
removed MSC codes
fixed typo in paper

Regularized discriminant analysis (\emph{RDA}) is a widely popular classifier
that lacks interpretability and is impractical for high-dimensional data. Here,
we present a competing classifier called high-dimensional \emph{RDA}
(\emph{HDRDA}), designed for the small-sample, high-dimensional setting. For
\emph{HDRDA}, we show that each training observation, regardless of class,
contributes to the class covariance matrix, resulting in an interpretable
estimator that \emph{borrows} from the pooled sample covariance
matrix. Moreover, we show that \emph{HDRDA} is equivalent to a classifier in a
reduced-feature space with dimension approximately equal to the sample
size. Consequently, the matrix operations employed by \emph{HDRDA} are linear
in the number of features. Timing comparisons between \emph{HDRDA} and RDA
establish that as the number of features increases, the computational runtime
of \emph{HDRDA} is drastically smaller than that of \emph{RDA}. Also, we
demonstrate that \emph{HDRDA} often attains superior classification accuracy to
several sparse and regularized classifiers using three artificial and six real
high-dimensional datasets.

@@

% TODO: Are MSC codes needed?: \MSC[2010] 62H30\sep 65F15\sep 65F20\sep 65F22

>>>>

Regularized discriminant analysis (\emph{RDA}) is a widely popular classifier
that lacks interpretability and is impractical for high-dimensional data. Here,
we present a competing classifier called high-dimensional \emph{RDA}
(\emph{HDRDA}), designed for the small-sample, high-dimensional setting. For
\emph{HDRDA}, we show that each training observation, regardless of class,
contributes to the class covariance matrix, resulting in an interpretable
estimator that \emph{borrows} from the pooled sample covariance
matrix. Moreover, we show that \emph{HDRDA} is equivalent to a classifier in a
reduced-feature space with dimension approximately equal to the sample
size. Consequently, the matrix operations employed by \emph{HDRDA} are linear
in the number of features. Timing comparisons between \emph{HDRDA} and \emph{RDA}
establish that as the number of features increases, the computational runtime
of \emph{HDRDA} is drastically smaller than that of \emph{RDA}. Also, we
demonstrate that \emph{HDRDA} often attains superior classification accuracy to
several sparse and regularized classifiers using three artificial and six real
high-dimensional datasets.

@@
